---
title: "esm206-lab8-ac"
author: "Annie Combs"
date: "November 15, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(modelsummary)
library(broom)
library(stargazer)
library(corrplot)
```

```{r}
homes <- read_csv(here("data", "slo_homes (1).csv"))

# Make a subset of homes called homes_sub that only contains observations from San Luis Obispo, Arroyo Grande, Atascadero, Santa Maria-Orcutt

homes_sub <- homes %>%
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Santa Maria-Orcutt", "Atascadero"))
```
## Explore our data

Summary stas for home price based on city and sale status

Find and return in a nice summary table the mean and standard deviation of home price grouped by city and sale status

```{r}

# set eval = FALSE and your code won't even run

homes_explore <- homes_sub %>%
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price), sd_price = sd(Price))

homes_explore

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
```

##### Explore the relationship betwen square footage and home price
Change the point color by city and the point shape by sale status

```{r}

ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status))+
  geom_smooth(method = lm)
```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

plot(homes_lm1)
```

### Use corrplot to find correlations between variables

```{r}
# make a subset that only contains quantitative variables

homes_quant <- homes_sub %>%
  select(Price:PricePerSqFt)

homes_corr <- cor(homes_quant)

homes_corr

corrplot(homes_corr)
```

make a new model where you only use these predictor variables: City, SqFt, Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

homes_lm2

plot(homes_lm2)
```
#### 84% of variance in price is explained by the predictor variables in model 1 (ran summary(homes_lm1 in the console))

Find the AIC value of each model

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think might make sense and then check out and compare the model fit, outputs, and AIC value.

```{r}
homes_lm3 <- lm(PricePerSqFt ~ Price + SqFt + City, data = homes_sub)

homes_lm3

plot(homes_lm3)

```

```{r}
AIC(homes_lm3)
```

Use modelsummary() to show model outputs side by side

If you use modelsummary() it wants to return model outputs of multiple models, it wants you to feed it to it as a list.

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model

Use brrom::augment to show what the predicted values are for the existing data set

```{r}
homes_predicted <- augment(homes_lm1)
```

Use predict() to try out your model on new scenarios that you create